Structured Versus Decorated Cospans

### 2020-12-04 cospans.tex
Changed the direction of the chi's

\begin{defn}
\label{defn:symmetric_monoidal_double_category}
A \define{symmetric monoidal double category} is a symmetric pseudomonoid in $\Dbl$. 
\end{defn}
\noindent
Explicitly, a symmetric monoidal double category is a monoidal double category $\lD$ such that:
\begin{itemize}
		\item $\lD_0$ and $\lD_1$ are symmetric monoidal categories, with braidings both denoted $\beta$.
		\item The functors $S$ and $T$ are symmetric strict monoidal functors.
		\item The following diagrams commute, expressing that the braiding is a transformation of double categories:
		\begin{equation}
		\begin{tikzpicture}\label{eq:braidingaxiom}
			\node (A) at (0,1.5) {\footnotesize{$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$}};
			\node (A') at (0,0) {\footnotesize{$ (M_2\otimes N_2)\odot (M_1\otimes N_1)$}};
			\node (B) at (5,1.5) {\footnotesize{$(N_2\odot N_1) \otimes (M_2\odot M_1)$}};
			\node (B') at (5,0) {\footnotesize{$ (N_2 \otimes M_2)\odot (N_1 \otimes M_1)$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\chi$} (A')
				(A) edge node[above]{$\beta$} (B)
				(B) edge node[right]{$\chi$} (B')
				(A') edge node[above]{$\beta \odot \beta$} (B');
		\end{tikzpicture}
		%
		\quad
		%
		\begin{tikzpicture}
			\node (A) at (0,1.5) {\footnotesize{$U_A \otimes U_B$}};
			\node (A') at (0,0) {\footnotesize{$U_B\otimes U_A$}};
			\node (B) at (2,1.5) {\footnotesize{$U_{A\otimes B} $}};
			\node (B') at (2,0) {\footnotesize{$U_{B\otimes A}$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\beta$} (A')
				(B) edge node[above]{$\mu$} (A)
				(B) edge node[right]{$U_\beta$} (B')
				(B') edge node[above]{$\mu$} (A');
		\end{tikzpicture}
		\end{equation}
\end{itemize}

@@

Here we show a sample check of a coherence law for the proof of \cref{DC}.
All relevant structure for decorated cospans is as described in \cref{thm:decorated_cospans,DC}. The coherence law that we check says that this diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$};
\node (B) at (3,0) {$(N_2 \odot N_1) \otimes (M_2 \odot M_1)$};
\node (C) at (0,-.75) {$(M_2 \otimes N_2) \odot (M_1 \otimes N_1)$};
\node (D) at (3,-.75) {$(N_2 \otimes M_2) \odot (N_1 \otimes M_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\beta$} (B)
(B) edge node[right]{$\chi$} (D)
(A) edge node[left]{$\chi$} (C)
(C) edge node[above]{$\beta \odot \beta$} (D);
\end{tikzpicture}
\]
{\chris $\chi$'s in the definition of a monoidal double category have a different direction. Since it is an isomorphism it doesn't really change anything, but consider changing to keep them right}
First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide:
\[
		\begin{tikzpicture}
			\node (a) at (-4,0) {$a+a'$};
			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
			\node (c) at (6,0) {$c+c'$};
			\node (a2) at (-4,1) {$a'+a$};
			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
			\node (c2) at (6,1) {$c'+c$};
            \node (a3) at (-4,2) {$a'+a$};
			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
			\node (c3) at (6,2) {$c'+c$};
            \node (a5) at (-4,-1) {$a+a'$};
			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
			\node (c5) at (6,-1) {$c+c'$};
            \node (a6) at (-4,-2) {$a'+a$};
			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
			\node (c6) at (6,-2) {$c'+c$};
			\path[->,font=\scriptsize,>=angle 90]
			(a) edge node[above]{$$} (b)
			(c) edge node[above]{$$} (b)
            (a2) edge node[above]{$$} (b2)
			(c2) edge node[above]{$$} (b2)
            (a) edge node[left]{$\beta$} (a2)
            (b) edge node[left]{$\beta$} (b2)
%(b) edge node[right]{$\tau_1$} (b2)
			(c) edge node[right]{$\beta$} (c2)
            (a3) edge node[above]{$$} (b3)
			(c3) edge node[above]{$$} (b3)
            (a2) edge node[left]{$1$} (a3)
            (b2) edge node[left]{$\hat{\chi}$} (b3)
%(b2) edge node[right]{$\tau_2$} (b3)
			(c2) edge node[right]{$1$} (c3)
            (a5) edge node[above]{$$} (b5)
			(c5) edge node[above]{$$} (b5)
            (a) edge node[left]{$1$} (a5)
            (b) edge node[left]{$\hat{\chi}$} (b5)
%(b) edge node[right]{$\tau_4$} (b5)
			(c) edge node[right]{$1$} (c5)
            (a6) edge node[above]{$$} (b6)
			(c6) edge node[above]{$$} (b6)
            (a5) edge node[left]{$\beta$} (a6)
            (b5) edge node[left]{$\beta \odot \beta$} (b6)
 %(b5) edge node[right]{$\tau_5$} (b6)
			(c5) edge node[right]{$\beta$} (c6);
		\end{tikzpicture}
	\]
where $\beta$ is the braiding of the symmetric monoidal category $\A$, $\hat{\chi}$ is the globular 2-morphism interchanging the tensor product and horizontal composition of the symmetric monoidal double category $\lCsp(\A)$, and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.

@@

			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
			\node (c) at (8,0) {$(x_1 \odot x_2) \oplus (y_1 \odot y_2) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};

@@

			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
			\node (c2) at (8,1) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};

@@

			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
			\node (c3) at (8,2) {$(y_1\oplus x_1) \odot (y_2\oplus x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};

@@

			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
			\node (c5) at (8,-1) {$(x_1\oplus y_1) \odot (x_2\oplus y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};

@@

			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
			\node (c6) at (8,-2) {$(y_1\oplus x_1) \odot (y_2\oplus x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};

@@

                                (b) edge node[left]{$\beta$} (b2)

@@

                                (b5) edge node[left]{$\beta \odot \beta$} (b6)

@@

\node (A) at (0,0) {$\tau_1 \colon F(\beta)((x_1 \odot x_2)\oplus(y_1 \odot y_2)) \to (y_1 \odot y_2)\oplus(x_1 \odot x_2)$};
\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_1 \odot y_2)\oplus(x_1 \odot x_2)) \to (y_1\oplus x_1) \odot (y_2\oplus x_2)$};
\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_1 \odot x_2)\oplus(y_1 \odot y_2)) \to (x_1\oplus y_1) \odot (x_2\oplus y_2)$};
\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta \odot \beta)((x_1\oplus y_1)\odot(x_2\oplus y_2)) \to (y_1\oplus x_1)\odot(y_2\oplus x_2)$};

@@

These decoration isomorphisms then form the following commutative diagram in the category $F((n_1+m_1)+_{b'+b}(n_2+m_2))$:
\node (A) at (0,0) {$F(\hat{\chi} \beta)((x_1 \odot x_2)\oplus(y_1 \odot y_2))$};
\node (B) at (4,0) {$F(\hat{\chi})((y_1 \odot y_2)\oplus(x_1 \odot x_2))$};
\node (C) at (0,-1) {$F(\beta \odot \beta)((x_1\oplus y_1) \odot (x_2 \oplus  y_2))$};
\node (D) at (4,-1) {$(y_1\oplus x_1) \odot (y_2\oplus x_2)$};

@@

(A) edge node[left]{$F(\beta \odot \beta)(\tau_3)$} (C)

@@

where in the top left corner, we note that $$F(\hat{\chi} \beta)((x_1 \odot x_2)\oplus (y_1 \odot y_2)) = F((\beta \odot \beta)\hat{\chi})((x_1 \odot x_2)\oplus (y_1 \odot y_2))$$

>>>>

\begin{defn}
\label{defn:symmetric_monoidal_double_category}
A \define{symmetric monoidal double category} is a symmetric pseudomonoid in $\Dbl$. 
\end{defn}
\noindent
Explicitly, a symmetric monoidal double category is a monoidal double category $\lD$ such that:
\begin{itemize}
		\item $\lD_0$ and $\lD_1$ are symmetric monoidal categories, with braidings both denoted $\beta$.
		\item The functors $S$ and $T$ are symmetric strict monoidal functors.
		\item The following diagrams commute, expressing that the braiding is a transformation of double categories:
		\begin{equation}
		\begin{tikzpicture}\label{eq:braidingaxiom}
			\node (A) at (0,1.5) {\footnotesize{$ (M_2\otimes N_2)\odot (M_1\otimes N_1)$}};
			\node (A') at (0,0) {\footnotesize{$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$}};
			\node (B) at (5,1.5) {\footnotesize{$ (N_2 \otimes M_2)\odot (N_1 \otimes M_1)$}};
			\node (B') at (5,0) {\footnotesize{$(N_2\odot N_1) \otimes (M_2\odot M_1)$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\chi$} (A')
				(A) edge node[above]{$\beta \odot \beta$} (B)
				(B) edge node[right]{$\chi$} (B')
				(A') edge node[above]{$\beta$} (B');
		\end{tikzpicture}
		%
		\quad
		%
		\begin{tikzpicture}
			\node (A) at (0,1.5) {\footnotesize{$U_A \otimes U_B$}};
			\node (A') at (0,0) {\footnotesize{$U_B\otimes U_A$}};
			\node (B) at (2,1.5) {\footnotesize{$U_{A\otimes B} $}};
			\node (B') at (2,0) {\footnotesize{$U_{B\otimes A}$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\beta$} (A')
				(B) edge node[above]{$\mu$} (A)
				(B) edge node[right]{$U_\beta$} (B')
				(B') edge node[above]{$\mu$} (A');
		\end{tikzpicture}
		\end{equation}
\end{itemize}

@@

Here we show a sample check of a coherence law for the proof of \cref{DC}.
All relevant structure for decorated cospans is as described in \cref{thm:decorated_cospans,DC}. The coherence law that we check says that this diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_2 \otimes N_2) \odot (M_1 \otimes N_1)$};
\node (B) at (3,0) {$(N_2 \otimes M_2) \odot (N_1 \otimes M_1)$};
\node (C) at (0,-.75) {$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$};
\node (D) at (3,-.75) {$(N_2 \odot N_1) \otimes (M_2 \odot M_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\beta \odot \beta$} (B)
(B) edge node[right]{$\chi$} (D)
(A) edge node[left]{$\chi$} (C)
(C) edge node[above]{$\beta$} (D);
\end{tikzpicture}
\]
{\chris $\chi$'s in the definition of a monoidal double category have a different direction. Since it is an isomorphism it doesn't really change anything, but consider changing to keep them right}
First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide:
\[
		\begin{tikzpicture}
			\node (a) at (-4,0) {$a+a'$};
			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
			\node (c) at (6,0) {$c+c'$};
			\node (a2) at (-4,1) {$a'+a$};
			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
			\node (c2) at (6,1) {$c'+c$};
            \node (a3) at (-4,2) {$a'+a$};
			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
			\node (c3) at (6,2) {$c'+c$};
            \node (a5) at (-4,-1) {$a+a'$};
			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
			\node (c5) at (6,-1) {$c+c'$};
            \node (a6) at (-4,-2) {$a'+a$};
			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
			\node (c6) at (6,-2) {$c'+c$};
			\path[->,font=\scriptsize,>=angle 90]
			(a) edge node[above]{$$} (b)
			(c) edge node[above]{$$} (b)
            (a2) edge node[above]{$$} (b2)
			(c2) edge node[above]{$$} (b2)
            (a) edge node[left]{$\beta$} (a2)
            (b) edge node[left]{$\beta \odot \beta$} (b2)
%(b) edge node[right]{$\tau_1$} (b2)
			(c) edge node[right]{$\beta$} (c2)
            (a3) edge node[above]{$$} (b3)
			(c3) edge node[above]{$$} (b3)
            (a2) edge node[left]{$1$} (a3)
            (b2) edge node[left]{$\hat{\chi}$} (b3)
%(b2) edge node[right]{$\tau_2$} (b3)
			(c2) edge node[right]{$1$} (c3)
            (a5) edge node[above]{$$} (b5)
			(c5) edge node[above]{$$} (b5)
            (a) edge node[left]{$1$} (a5)
            (b) edge node[left]{$\hat{\chi}$} (b5)
%(b) edge node[right]{$\tau_4$} (b5)
			(c) edge node[right]{$1$} (c5)
            (a6) edge node[above]{$$} (b6)
			(c6) edge node[above]{$$} (b6)
            (a5) edge node[left]{$\beta$} (a6)
            (b5) edge node[left]{$\beta$} (b6)
 %(b5) edge node[right]{$\tau_5$} (b6)
			(c5) edge node[right]{$\beta$} (c6);
		\end{tikzpicture}
	\]
where $\beta$ is the braiding of the symmetric monoidal category $\A$, $\hat{\chi}$ is the globular 2-morphism interchanging the tensor product and horizontal composition of the symmetric monoidal double category $\lCsp(\A)$, and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.

@@

			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
			\node (c) at (8,0) {$(x_1\oplus y_1) \odot (x_2\oplus y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};

@@

			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
			\node (c2) at (8,1) {$(y_1\oplus x_1) \odot (y_2\oplus x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};

@@

			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
			\node (c3) at (8,2) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};

@@

			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
			\node (c5) at (8,-1) {$(x_1 \odot x_2) \oplus (y_1 \odot y_2) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};

@@

			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
			\node (c6) at (8,-2) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};

@@

                                (b) edge node[left]{$\beta \odot \beta$} (b2)

@@

                                (b5) edge node[left]{$\beta$} (b6)

@@

\node (A) at (0,0) {$\tau_1 \colon F(\beta \odot \beta)((x_1\oplus y_1)\odot(x_2\oplus y_2)) \to (y_1\oplus x_1)\odot(y_2\oplus x_2)$};
\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_1 \oplus x_1)\odot(y_2 \oplus x_2)) \to (y_1\odot y_2) \oplus (x_1\odot x_2)$};
\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_1 \oplus y_1)\odot(x_2 \oplus y_2)) \to (x_1\odot x_2) \oplus (y_1\odot y_2)$};
\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta)((x_1\odot x_2)\oplus(y_1\odot y_2)) \to (y_1\odot y_2)\oplus(x_1\odot x_2)$};

@@

These decoration isomorphisms then form the following commutative diagram in the category $F({(n_1+_{b'}n_2)}+{(m_1+_b m_2)})$:
\node (A) at (0,0) {$F(\hat{\chi} (\beta \odot \beta))((x_1 \oplus y_1)\odot(x_2 \oplus y_2))$};
\node (B) at (4,0) {$F(\hat{\chi})((y_1 \oplus x_1)\odot(y_2 \oplus x_2))$};
\node (C) at (0,-1) {$F(\beta)((x_1\odot x_2) \oplus (y_1 \odot y_2))$};
\node (D) at (4,-1) {$(y_1\odot y_2) \oplus (x_1\odot x_2)$};

@@

(A) edge node[left]{$F(\beta)(\tau_3)$} (C)

@@

where in the top left corner, we note that $$F(\hat{\chi} (\beta \odot \beta))((x_1 \oplus y_1)\odot(x_2 \oplus y_2)) = F(\beta\hat{\chi})((x_1 \oplus y_1)\odot (x_2 \oplus y_2))$$
